### 2012-06-05 docs/architecture/architecture.tex
fix compiling
add note about BCs
update the build documentation

Problems piece together various \maestro\ directories, choosing a
reaction network, equation of state, and conductivity routine to build
an executable.  Briefly, the \maestro\ sub-directories are:
\begin{itemize}
\item {\tt extern/}

  External modules, like ODE integrators, equations of state, reaction
  networks, etc.  Many of these routines were developed by other groups.

  Important sub-directories include:

@@

  \item {\tt initial\_models}

    Several sub-directories containing routines to generate 1D initial
    conditions in hydrostatic equilibrium for mapping onto the
    \maestro\ grid.  See \S~\ref{sec:initial_models} for details.

@@

  \item {\tt Source}

@@

  \item {\tt Source_SDC}

@@

  \item {\tt TEST\_PROBLEMS}

@@

  \item {\tt UNIT\_TESTS}

@@

@@

The next line defines where the top of the source tree is located.
\begin{lstlisting}[language={[gnu]make},mathescape=false]
  FPARALLEL := ../..
\end{lstlisting}

A \maestro\ application is built from several packages (the
multigrid solver, an EOS, a reaction network, etc.).  The core
\maestro\ packages are always included, so a problem only needs
to define the EOS, reaction network, and conductivities to
use, as well as any extra, problem-specific files.  
\begin{lstlisting}[language={[gnu]make},mathescape=false]
EOS_DIR := extern/EOS/helmeos   
CONDUCTIVITY_DIR := extern/conductivity/constant
NETWORK_DIR := extern/networks/ignition

EXTRA_DIR := extern/random
\end{lstlisting}
Generally, one does not need to include the problem directory itself
in {\tt EXTRA\_DIR}, unless there are unique source files found there,
described in a {\tt GPackage.mak} file.  These variables are
interpreted by the {\tt GMaestro.mak} file and used to build a master
list of packages called {\tt Fmdirs}.  The build system will attempt
to build all of the files listed in the various {\tt GPackage.mak}
files found in the {\tt Fmdirs} directories.  Furthermore, {\tt
  Fmdirs} will be will be added to the {\tt make} {\tt VPATH}, which
is the list of directories to search for source files.  The problem
directory will always be put first in the {\tt VPATH}, so any source
files placed there override those with the same name found elsewhere
in the source tree.

@@

The final line in the {\tt GNUmakefile} includes the rules to actually
build the executable.
\begin{lstlisting}[language={[gnu]make},mathescape=false]
  include $(FPARALLEL)/MAESTRO/GMaestro.mak
\end{lstlisting}
%$

@@

The actual filling of the ghostcells according to the descriptions
contained in the \bctower\ is carried out by the {\tt multifab\_physbc}
routine.

>>>>

Problems piece together various \maestro\ directories, choosing a
reaction network, equation of state, and conductivity routine to build
an executable.  Briefly, the \maestro\ sub-directories are:

@@

  \item {\tt Microphysics/}

    The core microphysics routines used by \maestro.  These are organized
    into the following sub-directories.

@@

  \item {\tt Source/}

@@

  \item {\tt Source\_SDC/}

@@

  \item {\tt TEST\_PROBLEMS/}

@@

  \item {\tt UNIT\_TESTS/}

@@

  \item {\tt Util/}

    Various helper routines exist in this directory.  Some of these
    are externally developed.

    \item {\tt BLAS/}

      Linear algebra routines.

    \item {\tt random/}

      A random number generator.

@@

The next line defines where the top of the \maestro\ source tree is located.
\begin{lstlisting}[language={[gnu]make},mathescape=false]
  MAESTRO_TOP_DIR := ../..
\end{lstlisting}

A \maestro\ application is built from several packages (the
multigrid solver, an EOS, a reaction network, etc.).  The core
\maestro\ packages are always included, so a problem only needs
to define the EOS, reaction network, and conductivities to
use, as well as any extra, problem-specific files.  
\begin{lstlisting}[language={[gnu]make},mathescape=false]
EOS_DIR := helmeos   
CONDUCTIVITY_DIR := constant
NETWORK_DIR := ignition_simple

EXTRA_DIR := Util/random
\end{lstlisting}
Note that the microphysics packages are listed simply by the name of 
the directory containing the specific implementation (e.g. {\tt helmeos}).
By default, the build system will look in {\tt Microphysics/EOS/} for
the EOS, {\tt Microphysics/conductivity/} for the conductivity routine,
and {\tt Microphysics/networks/} for the reaction network.  To
override this default search path, you can set {\tt EOS\_TOP\_DIR},
{\tt CONDUCTIVITY\_TOP\_DIR}, and {\tt NETWORK\_TOP\_DIR} respectively.

Generally, one does not need to include the problem directory itself
in {\tt EXTRA\_DIR}, unless there are unique source files found there,
described in a {\tt GPackage.mak} file.  These variables are
interpreted by the {\tt GMaestro.mak} file and used to build a master
list of packages called {\tt Fmdirs}.  The build system will attempt
to build all of the files listed in the various {\tt GPackage.mak}
files found in the {\tt Fmdirs} directories.  Furthermore, {\tt
  Fmdirs} will be will be added to the {\tt make} {\tt VPATH}, which
is the list of directories to search for source files.  The problem
directory will always be put first in the {\tt VPATH}, so any source
files placed there override those with the same name found elsewhere
in the source tree.

@@

The final line in the {\tt GNUmakefile} includes the rules to actually
build the executable.
\begin{lstlisting}[language={[gnu]make},mathescape=false]
  include $(MAESTRO_TOP_DIR)/GMaestro.mak
\end{lstlisting}
%$

@@

The actual filling of the ghostcells according to the descriptions
contained in the \bctower\ is carried out by the {\tt
  multifab\_physbc} routine.  When you have an {\tt EXT\_DIR}
condition in {\tt multifab\_physbc} (an specified in the inputs file
as {\tt inlet}), the advection solver (via the slope routine) and
linear solvers will then assume that the value in the ghost cells is
equal to the value that actually lies on the wall.
